Constraining the Interiors of Asteroids Through Close Encounters

### 2022-03-26 paper/main.tex
Prepared cadence measured vs speed

\cite{MOSKOVITZ2020113519}

@@

@@

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

@@

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

@@

The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS. Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article. The statement may refer to original data generated in the course of the study or to third-party data analysed in the article. The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.

>>>>

\jtd{Write}

@@

\jtd{Write}

@@

\jtd{Write}
The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

@@

\jtd{Write}
The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

@@

The code used to generate data, fit density moments to it, and extract density distributions from the moments is available on \href{https://github.com/jack-dinsmore/asteroid-tidal-torque}{GitHub}, or by contacting JTD.
